---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
[![Travis-CI Build Status](https://travis-ci.org/mdsumner/unjoin.svg?branch=master)](https://travis-ci.org/mdsumner/unjoin)

# unjoin

The goal of unjoin is to provide `unjoin` for data frames. 

## Installation

You can install unjoin from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("mdsumner/unjoin")
```

## Example

This is a basic example which shows you how to unjoin a data frame. 

```{r example}
library(unjoin)

unjoin(iris)

library(dplyr)
iris %>% unjoin(Species)

iris %>% unjoin(Species, Petal.Width)
```

This is used to build topological data structures, with a
kind of inside-out version of a nested data frame. Whether it's of broader use is unclear. 



Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

