---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![Travis-CI Build Status](https://travis-ci.org/hypertidy/unjoin.svg?branch=master)](https://travis-ci.org/hypertidy/unjoin)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/mdsumner/unjoin?branch=master&svg=true)](https://ci.appveyor.com/project/mdsumner/unjoin)
[![Coverage Status](https://img.shields.io/codecov/c/github/hypertidy/unjoin/master.svg)](https://codecov.io/github/hypertidy/unjoin?branch=master)
 [![CRAN status](https://www.r-pkg.org/badges/version/unjoin)](https://CRAN.R-project.org/package=unjoin)
 
# unjoin

The goal of unjoin is to provide `unjoin` for data frames. This is exactly part of what `tidyr::nest` does, but with two differences: 

* the split data frames are not nested, they are split and returned as two whole tibbles `main` and `data`
* there is an explicit key column added to identify the de-duplicated rows in `main` with the rows in `data`. 

## Installation

Install unjoin from CRAN: 

```{r cran-installation, eval=FALSE}
install.packages("unjoin")
```
You can install the development unjoin from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("hypertidy/unjoin")
```

## Example

This is a basic example which shows you how to unjoin a data frame. 

```{r example}
library(unjoin)

unjoin(iris)

library(dplyr)
iris %>% unjoin(Species)

iris %>% unjoin(Species, Petal.Width)
```

This is used to build topological data structures, with a
kind of inside-out version of a nested data frame. Whether it's of broader use is unclear. 

There is a record here of some of  the thinking that led to unjoin: https://github.com/r-gris/babelfish

The function `unjoin` replaces the method here: http://rpubs.com/cyclemumner/iout_nest

```{r}
(d2 <- iris %>% unjoin(Species, Petal.Width))
```

We can chain unjoins together, but make sure not to repeat a `key_col` in one of these. 

```{r}
unjoin(iris, Species, key_col = "vertex") %>% unjoin(Petal.Width, vertex,  key_col = "branch")
```

Also, there's no escape hatch here, you can't "unjoin" your way to normal nirvana, each unjoin needs to carry the last unjoin-key with it, and you just end up with the big link table with no attributes. It needs some kind of group-semantic to cut the chain. 

---

Please note that this project is released with a [Contributor Code of Conduct](https://github.com/hypertidy/unjoin/blob/master/CONDUCT.md). By participating in this project you agree to abide by its terms.

